HO unification from object language to meta language

### 2024-04-04 paper/main.tex
tex solved a todo
tex: rewrite lemma progress-beta-L𝜆

\begin{definition}[\progBetaLL]
  A link \linkbetaM{\Gamma}{T}{\rhsBeta} is removed from \linkStore, if given
  the substitution $\sigma$, $\sigma l_1$ is a name, say $t$, such that, $t
  \notin s_1\dots s_n$. In this case, let $Y$ a fresh variable, then
  \linketaM{\Gamma}{X_{s_1\dots s_n}}{\lambda x.Y_{s_1\dots s_n,x}} is added to
  \linkStore, and 1) if $m = 1$ then $Y_{s_1\dots s_n, t}$ is unified with $T$,
  2) otherwise, the refined \linkbeta, \linkbetaM{\Gamma}{T}{M_{s_1\dots
  s_n,t}\appsep t_2\dots t_m}, is added to \linkStore.
  \label{def:progBetaLL}
  % \noteE[inline]{non è chiaro. la sostituzione immagino sia la corrente, non se ne esiste una. Poi non è chiaro se otherwise si riferische a in this case. Usa un enumerate}
  %\noteE[inline]{Is it clearer?}
  \noteE[inline]{l1 or t1? Forse è più chiaro dire che il ilnk beta viene raffinato con link beta cone meno argomenti, Se poi il numero di argomenti extra è 0 il tutto è in llambda e quindi viene buttato via. In questo modo la terminazione è ancora più chiara perchè si vede già che prima decresce la lista di argomenti e poi il numero di beta}
\end{definition}

@@

\noindent
Initially the \linkbeta \rhs is a variable $D$ applied to the $E_x$.
The first unification problem results in $\sigma =
\{A \mapsto \lambda x.x\}$. In turn this instantiation
triggers $\linkStore_1$ by \progressetaleft 
and $E$ is assigned to $\lambda x.x$.
Under this substitution the \linkbeta becomes
\linkbetaM{x}{C_x}{(D \appsep x)}, and by \progBetaLL
it is replaced with the following two links:
\linkbetaM{x}{C_x}{F_x} and
\noteE{ma allora il link ora sparisce perhè è in llambda?}
\linketaM{}{E}{\lambda x.D_x}. The second unification
problem assignes $f$ to $B$, that in turn activates
the second \linketa ($f$ is assigned to $C$), and then all the remaining links
are solved. The final \Ho substitution is $\sigma = \{A _{} \mapsto \lambda x.x, 
B _{} \mapsto f, C _{x} \mapsto (f\appsep x), 
D _{} \mapsto f, E _{x} \mapsto x, F _{x} \mapsto C_{x} \}$ and is decompiled into $\rho = \{X \mapsto \lambda x.x,
Y \mapsto f\}$.
\noteE{alla fine non si usa anche la regola beta-rigid-head?}

>>>>

\begin{definition}[\progBetaLL]
  Given a substitution $\sigma$ and a \linkbeta \linkbetaM{\Gamma}{T}{\rhsBeta}
  such that $\sigma t_1$ is a name, say $t$, and $t\notin s_1\dots s_n$. If $m =
  0$, then the \linkbeta is removed and \lhs is unified with \rhsBetaHead.
  If $m > 0$, then the \linkbeta is replaced by a refined version
  $\linkbetaM{\Gamma}{T}{Y_{s_1\dots s_n,t}\appsep t_2\dots t_m}$ with reduced
  list of arguments and $Y$ being a fresh variable. Moreover, the new \linkbeta,
  \linketaM{\Gamma}{X_{s_1\dots s_n}}{\lambda x.Y_{s_1\dots s_n,x}} is added to 
  \linkStore.

  % A link \linkbetaM{\Gamma}{T}{\rhsBeta} is removed from \linkStore, if given
  % the substitution $\sigma$, $\sigma t_1$ is a name, say $t$, such that, $t
  % \notin s_1\dots s_n$. In this case, let $Y$ a fresh variable, then
  % \linketaM{\Gamma}{X_{s_1\dots s_n}}{\lambda x.Y_{s_1\dots s_n,x}} is added to
  % \linkStore, and 1) if $m = 1$ then $Y_{s_1\dots s_n, t}$ is unified with $T$,
  % 2) otherwise, the refined \linkbeta, \linkbetaM{\Gamma}{T}{M_{s_1\dots
  % s_n,t}\appsep t_2\dots t_m}, is added to \linkStore.
  % \label{def:progBetaLL}
  % % \noteE[inline]{non è chiaro. la sostituzione immagino sia la corrente, non se ne esiste una. Poi non è chiaro se otherwise si riferische a in this case. Usa un enumerate}
  % %\noteE[inline]{Is it clearer?}
  % \noteE[inline]{l1 or t1? Forse è più chiaro dire che il ilnk beta viene raffinato con link beta cone meno argomenti, Se poi il numero di argomenti extra è 0 il tutto è in llambda e quindi viene buttato via. In questo modo la terminazione è ancora più chiara perchè si vede già che prima decresce la lista di argomenti e poi il numero di beta}
  \noteD{L'ho riformulato}
\end{definition}

@@

\noindent
Initially the \linkbeta \rhs is a variable $D$ applied to the $E_x$.
The first unification problem results in $\sigma =
\{A \mapsto \lambda x.x\}$. In turn this instantiation
triggers $\linkStore_1$ by \progressetaleft 
and $E$ is assigned to $\lambda x.x$.
Under this substitution the \linkbeta becomes
\linkbetaM{x}{C_x}{(D \appsep x)}, and by \progBetaLL
it is replaced with the link:
\linketaM{}{E}{\lambda x.D_x}, while $C_x$ is unified with $D_x$. The second unification
problem assignes $f$ to $B$, that in turn activates
the second \linketa ($f$ is assigned to $C$), and then all the remaining links
are solved. The final \Ho substitution is $\sigma = \{A _{} \mapsto \lambda x.x, 
B _{} \mapsto f, C _{x} \mapsto (f\appsep x), 
D _{} \mapsto f, E _{x} \mapsto x, F _{x} \mapsto C_{x} \}$ and is decompiled into $\rho = \{X \mapsto \lambda x.x,
Y \mapsto f\}$.
\noteE{alla fine non si usa anche la regola beta-rigid-head?}
\noteD{nope. Si risolve tutto by \progBetaLL}
